\section{Game Design Documentation}\label{game-design-documentation}

This document serves as a non-technical overview of the game's design.
Please note that any numbers mentioned here aren't final, but provide a
strong starting point, and illustrate the distance between values in
some cases.

\subsection{Level Structure}\label{level-structure}

The game will exist in two parts: combat encounters and shops. There are
10 combat encounters in the game, and a shop will follow each one,
excluding the final combat encounter.

\subsection{Combat Encounter Design}\label{combat-encounter-design}

When in a combat encounter, the game functions as turn-based. The player
will always move first. The player gains 15 magic points at the
beginning of each turn. The player will be able to see a simple
representation of their character and their undefeated opponent(s), as
well as a dialogue box/interface. This box has two purposes: to narrate
the scene (``You encounter a Fish Man!'', ``You were hit for 20 damage
point(s)'', ``You won the battle'', etc.), and to serve as the player's
interface, allowing the player to select from their available attack
abilities (with information such as magic cost and damage type). Once an
attack is selected, the player is prompted to select which opponent they
wish to damage. Following this, the opponent's turn takes place, where,
like the player, an opponent will select from one of their abilities to
use on the player.

\subsection{Damage Types}\label{damage-types}

Both the player and the enemies that they can encounter are affected
differently by different damage types. For example, if the player were
to cast a water-based spell at a ``Pyromancer'' enemy, the attack would
be more effective than if it were cast on a ``Fish Man'' enemy.

Each attack ability in the game has a damage type. The damage types are
as follows: Physical, Fire, Water, Thunder, Absolute.

Attacks of the Absolute type are always effective on any opponent.

\subsection{Attack Abilities}\label{attack-abilities}

When the game begins, the player character only has one attacking
ability -- that being ``Punch'', a low-damage physical move.

Attacks that are not physical all cost magic points. Different attack
abilities use different amounts of magic points.

Within the shop screens in between encounters, players can exchange
their coins earned in battle for attack abilities. They are as follows:

\begin{longtable}[]{@{}lllll@{}}
\toprule\noalign{}
Name & Shop Cost (coins) & Magic Points & Damage Type & Notes \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Absolute Pulse & 10 & 20 & Absolute & \\
Slash & 15 & 0 & Physical & more powerful than punch \\
Water Jet & 20 & 20 & Water & \\
Thunder Storm & 25 & 30 & Thunder & \\
Fire Ball & 30 & 40 & Fire & High damage \\
\end{longtable}

\subsection{Passive Abilities}\label{passive-abilities}

When the game begins, the player character will have no non-attack
abilities. These can also be purchased in the shop in between
encounters. The purpose of these abilities is to allow the player to
become stronger in non-attacking ways.

The names of these abilities are descriptive and simple.

\begin{longtable}[]{@{}ll@{}}
\toprule\noalign{}
Name & Shop Cost (coins) \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Physical Damage Resistance & 20 \\
Fire Damage Resistance & 10 \\
Water Damage Resistance & 5 \\
Thunder Damage Resistance & 5 \\
Improved Physical Damage & 20 \\
Improved Fire Damage & 15 \\
Improved Water Damage & 10 \\
Improved Thunder Damage & 10 \\
\end{longtable}

\subsection{Structure of Levels}\label{structure-of-levels}

The game is split into three distinct phases:

\textbf{Phase 1}, where players will be given simple encounters to teach
them the basic rules of the game. This phase ends with a boss at level
3. Players will only fight one enemy at a time in Phase 1. Each
encounter rewards the player with 10 coins.

\textbf{Phase 2}, where players must deal with a steady climb in
challenge. This phase ends with a boss at level 7. Players can encounter
two enemies at once in Phase 2. Each encounter rewards the player with
15 coins.

\textbf{Phase 3}, where players will have their skills put to the test
in highly difficult encounters. This phase ends with a boss at level 9
and a final boss at level 10. Players can encounter three enemies at a
time, in level 8 in particular. Each encounter rewards the player with
20 coins.

\subsection{Enemies Within Encounters}\label{enemies-within-encounters}

There are many enemies that the player will encounter within the game.
The range of enemies that can be encountered increases as the phases
increase.

\subsubsection{Phase 1 Enemies}\label{phase-1-enemies}

\paragraph{Goblin}\label{goblin}

\begin{itemize}
\tightlist
\item
  Health: Medium
\item
  Actions: Slash
\item
  Resistant to: None
\item
  Vulnerable to: None
\end{itemize}

\paragraph{Fish Man}\label{fish-man}

\begin{itemize}
\tightlist
\item
  Health: Medium
\item
  Actions: Punch, Water Jet
\item
  Resistant to: Water
\item
  Vulnerable to: Thunder
\end{itemize}

\paragraph{Pyromancer}\label{pyromancer}

\begin{itemize}
\tightlist
\item
  Health: Low
\item
  Actions: Fire Ball
\item
  Resistant to: Fire
\item
  Vulnerable to: Water
\end{itemize}

\paragraph{Evil Wizard (Boss)}\label{evil-wizard-boss}

\begin{itemize}
\tightlist
\item
  Health: Medium
\item
  Actions: Thunder Storm, Fire Ball
\item
  Resistant to: Immune to anything not Physical/Absolute
\item
  Vulnerable to: Physical, Absolute
\end{itemize}

\subsubsection{Phase 2 Enemies}\label{phase-2-enemies}

(All non-boss enemies that have appeared in Phase 1)

\paragraph{Armoured Goblin}\label{armoured-goblin}

\begin{itemize}
\tightlist
\item
  Health: High
\item
  Actions: Slash
\item
  Resistant to: Mundane, Fire, Water
\item
  Vulnerable to: Thunder
\end{itemize}

\paragraph{Ghost (Boss)}\label{ghost-boss}

\begin{itemize}
\tightlist
\item
  Health: High
\item
  Actions: Thunder Storm, Absolute Pulse, Fire Ball
\item
  Resistant to: Physical (fully immune)
\item
  Vulnerable to: Absolute
\end{itemize}

\subsubsection{Phase 3 Enemies}\label{phase-3-enemies}

(All non-boss enemies that have appeared in Phase 2)

\paragraph{Black Knight (Boss)}\label{black-knight-boss}

\begin{itemize}
\tightlist
\item
  Health: High
\item
  Actions: Slash
\item
  Resistant to: Physical
\item
  Vulnerable to: Thunder
\end{itemize}

\paragraph{Dragon (Final Boss)}\label{dragon-final-boss}

\begin{itemize}
\tightlist
\item
  Health: Very High
\item
  Actions: Slash, Fire Ball, Thunder Storm
\item
  Resistant to: Fire, Thunder
\item
  Vulnerable to: Absolute
\end{itemize}

\subsection{Shop Design}\label{shop-design}

The shop exists as a single screen. Four random abilities are presented
to the user, alongside their price, and whether they are an ``Attack''
or ``Passive''. Providing the player can afford the abilities, they will
be able to buy as many of the four as they please. Once the player
decides they are done, they can select ``Next Encounter'' and continue
the game.
