\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\setcounter{secnumdepth}{4}
\usepackage{titlesec}

\usepackage[backend=biber, style=ieee, sorting=none]{biblatex}
\addbibresource{bibliography.bib}
\usepackage[shortlabels]{enumitem}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true, allcolors=blue}
\usepackage[nameinlink,noabbrev,capitalize]{cleveref}
\usepackage{colortbl}
\usepackage[section]{placeins}
\usepackage{subcaption}
\usepackage{longtable}
\usepackage{caption}
\captionsetup{font=footnotesize}
\setlength{\parskip}{\baselineskip}
\setlength{\parindent}{0pt}
\usepackage{titlesec}
\titlespacing*{\section} {0pt}{3ex}{2ex}
\titlespacing*{\subsection} {0pt}{3ex}{2ex}
\titlespacing*{\subsubsection} {0pt}{3ex}{2ex}
\usepackage{pdfpages}
\setlist{nolistsep,leftmargin=*}

\usepackage{tocloft}
\setlength{\cftsecindent}{0pt}
\setlength{\cftsubsecindent}{1.2em}
\setlength{\cftsecnumwidth}{2.2em}
\setlength{\cftsubsecnumwidth}{3.0em}
\setcounter{tocdepth}{2}


%settings paragraph to allow heading 4
\titleformat{\paragraph}
  {\normalfont\normalsize\bfseries}
  {\theparagraph}
  {1em}
  {}

\titlespacing*{\paragraph}
  {0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}


\title{Telemetry Game Report\\[0.3em]
\large COM2020 - Project 7}
\author{Harry Taylor, Luca Pacitti, Emre Acarsoy, Tom Croft, Luca Croci, Will Finney, \\ Kazybek Khairulla}
\date{17/02/2026}
\begin{document}
Our prototype consists of five automated tests using the JUnit framework (version X.X.X).
These automated tests all test the behaviour of the TelemetryListener class, which processes telemetry events as they happen - fundamental to the core objective of our program.
Details on how to run these can be found in our Deployment Guide (deployment\_guide.pdf).

We have implemented three unit tests - these test that the userID, sessionID and timestamp fields of events are validated and handled correctly.
By supplying varying fields of Event objects with erroneous data, we have asserted that exceptions are handled by verifying the contents of the error message output to console.
When supplying all of these fields with typical data, we have asserted that no exception handling occurs, since no exceptions were thrown in these cases.

We have also implemented two integration tests - these test that telemetry events are written to file if the user has enabled telemetry, and vice versa.
By invoking the listener's method on a valid Event object, we have asserted that the file's length increased immediately after the event occurred if telemetry was enabled,
and that the file's length did not change if telemetry was disabled.
Any data read from or written to file in our test was done using temporary files, to avoid cluttering in the production files.

// TO DO - Discuss manual tests once done

\end{document}