\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\setcounter{secnumdepth}{4}
\usepackage{titlesec}

\usepackage[skip=6pt]{parskip}

\usepackage[backend=biber, style=ieee, sorting=none]{biblatex}
\addbibresource{bibliography.bib}
\usepackage[shortlabels]{enumitem}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true, allcolors=blue}
\usepackage[nameinlink,noabbrev,capitalize]{cleveref}
\usepackage{colortbl}
\usepackage[section]{placeins}
\usepackage{subcaption}
\usepackage{longtable}
\usepackage{comment}
\usepackage{caption}
\captionsetup{font=footnotesize}
\setlength{\parindent}{0pt}
\usepackage{titlesec}
\titlespacing*{\section} {0pt}{3ex}{2ex}
\titlespacing*{\subsection} {0pt}{3ex}{2ex}
\titlespacing*{\subsubsection} {0pt}{3ex}{2ex}
\usepackage{pdfpages}
\setlist{nolistsep,leftmargin=*}

\usepackage{tocloft}
\setlength{\cftsecindent}{0pt}
\setlength{\cftsubsecindent}{1.2em}
\setlength{\cftsecnumwidth}{2.2em}
\setlength{\cftsubsecnumwidth}{3.0em}
\setcounter{tocdepth}{2}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}
{}
{0pt}
{}

\usepackage{booktabs}

\usepackage{float}
\usepackage{tabularx}

\title{Telemetry Game Report\\[0.3em]
\large COM2020 - Project 7}
\author{Emre Acarsoy, Luca Croci, Tom Croft, Will Finney, Kazybek Khairulla, Luca Pacitti, \\ Harry Taylor}
\date{\today}
\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Overview}
In this document we will outline all data stores used by the application. For each data store we will provide an overview, then detail its schema and the domain of all fields. When specifying the domain the type will be given, along with any other information in brackets.  We will then explain which applications use the data store, what fields they access, when, and for what purpose.

\section{Telemetry Event Logs}
\subsection{Overview}
Both simulation and user-generated telemetry is stored in the same format in two separate files. User-generated telemetry is stored in \verb|telemetry_events.json|. Simulation-generated data is stored in \verb|simulation_events.json|. All the stored data follows the telemetry schema specified in the report, which is duplicated here.
\subsection{Fields}
The log stores the events as a JSON list. Each event has several standard fields, and some feature optional fields.
\begin{table}[H]
  \begin{center}
    \begin{tabularx}{\textwidth}{
        | >{\centering\arraybackslash\hsize=0.25\hsize}X
      | >{\centering\arraybackslash\hsize=0.75\hsize}X |}
      \hline
      \textbf{Field} & \textbf{Domain}  \\
      \hline
      event & String (One of: StartSession, NormalEncounterStart, NormalEncounterComplete, NormalEncounterFail, BossEncounterStart, BossEncounterComplete, BossEncounterFail, GainCoin, BuyUpgrade, EndSession, SettingsChange, KillEnemy)  \\
      \hline
      userID & String \\
      \hline
      sessionID & Integer \\
      \hline
      timestamp & String (In the format \verb|YYYY/MM/DD/HH/MM/SS|) \\
      \hline
      difficulty & String (One of: Easy, Medium, Hard) \\
      \hline
      encounter\_name & String (One of: GoblinEncounter, FishManEncounter, PyromancerEncounter, EvilWizardEncounter, GoblinDuoEncounter, GoblinFishManEncounter, PyromancerFishManEncounter, GhostEncounter, ArmouredGoblinPyromancerEncounter, GoblinFishManPyromancerEncounter, BlackKnightEncounter, DragonEncounter) \\
      \hline
      stage\_number & Integer (In range [1, 10]) \\
      \hline
      player\_HP\_remaining & Non-negative integer \\
      \hline
      lives\_left & Positive integer \\
      \hline
      coins\_gained & Positive integer \\
      \hline
      coins\_spent & Positive integer \\
      \hline
      setting & String (One of: TelemetryEnabled, PlayerMaxHealth, EnemyDamageMultiplier, EnemyMaxHealthMultiplier, StartingLives, MaxMagic, MagicRegenRate, ShopItemCount) \\
      \hline
      setting\_value & String (Domain is that of the setting) \\
      \hline
      enemy\_type & String (One of: Goblin, Fishman, Pyromancer, EvilWizard, ArmouredGoblin, Ghost, BlackKnight, Dragon)\\
      \hline
      upgrade\_bought & String (One of: PhysicalDamageResistance, FireDamageResistance, WaterDamageResistance, ThunderDamageResistance, ImprovedPhysicalDamage, ImprovedFireDamage, ImprovedWaterDamage, ImprovedThunderDamage, SlashUnlock, AbsolutePulseUnlock, WaterJetUnlock, FireBallUnlock, ThunderStormUnlock) \\
      \hline
    \end{tabularx}
    \caption{Field definitions}
  \end{center}
\end{table}

\begin{table}[H]
  \begin{center}
    \begin{tabularx}{\textwidth}{
        | >{\centering\arraybackslash\hsize=0.4\hsize}X
      | >{\centering\arraybackslash\hsize=0.6\hsize}X |}
      \hline
      \textbf{Telemetry Event} & \textbf{Fields}  \\
      \hline
      StartSession & userID, sessionID, timestamp, event, difficulty \\
      \hline
      NormalEncounterStart & userID, sessionID, timestamp, encounter\_name, difficulty, stage\_number, event \\
      \hline
      NormalEncounterComplete & userID, sessionID, timestamp, encounter\_name, difficulty, stage\_number, event, player\_HP\_remaining \\
      \hline
      NormalEncounterFail & userID, sessionID, timestamp, encounter\_name, difficulty, stage\_number, event, lives\_left \\
      \hline
      BossEncounterStart & userID, sessionID, timestamp, encounter\_name, difficulty, stage\_number, event \\
      \hline
      BossEncounterComplete & userID, sessionID, timestamp, encounter\_name, difficulty, stage\_number, event, player\_HP\_remaining \\
      \hline
      BossEncounterFail & userID, sessionID, timestamp, encounter\_name, difficulty, stage\_number, event, lives\_left \\
      \hline
      GainCoin & userID, sessionID, timestamp, encounter\_name, difficulty, stage\_number, event, coins\_gained \\
      \hline
      BuyUpgrade & userID, sessionID, timestamp, stage\_number, event, upgrade\_bought, coins\_spent \\
      \hline
      EndSession & userID, sessionID, timestamp, event \\
      \hline
      SettingsChange & userID, timestamp, setting, setting\_value, event \\
      \hline
      KillEnemy & userID, sessionID, timestamp, encounter\_name, difficulty, stage\_number, enemy\_type, event \\
      \hline
    \end{tabularx}
    \caption{Event definitions}
  \end{center}
\end{table}

\subsection{Integrations}

\subsubsection{Java application}
The Java application only ever writes to the files. When running a simulation, all events are written to the simulation store and otherwise are written to the user store. Each event is written when generated by its source, as long as the user has telemetry enabled. Below is a description of what causes each event to be written.
\begin{itemize}
  \item StartSession - When a run is started
  \item NormalEncounterStart - When an encounter for stages 1, 2, 4, 5, 7 or 8 is started. These are normal encounters, consisting of one or more weak enemies.
  \item NormalEncounterComplete - When a normal encounter is completed by killing all enemies.
  \item NormalEncounterFail - When a normal encounter is failed by the player's health being reduced to zero.
  \item BossEncounterStart - When an encounter for stages 3, 6, 9, or 10 is started. These are boss encounters, consisting of one strong enemy.
  \item BossEncounterComplete - When a boss encounter is completed by killing the boss.
  \item BossEncounterFail -  When a boss encounter is failed by the player's health being reduced to zero.
  \item GainCoin - When the player gains any number of coins (which occurs at the end of an encounter).
  \item BuyUpgrade - When the player buys an upgrade in the shop (which they visit after each encounter)
  \item EndSession - When a run is completed, either by the player running out of lives, or completing stage 10.
  \item SettingsChange - When a setting (Either a design parameter, or whether telemetry is enabled) is changed by the user.
  \item KillEnemy - When an enemy is killed by the player in an encounter.
\end{itemize}

\subsubsection{Python application}
The python application only ever reads the files. It does so when a user logs in, and every 3 seconds from that point to allow real time viewing. It uses this data to make design suggestions and display dashboard views.

\section{Decision Log}
\subsection{Overview}
The decision log is used to store design parameter tweaks and justifications as to why.
%TODO
\subsection{Fields}

\subsection{Integrations}

\section{Settings File}

\subsection{Overview}
This file stores the values of the current value of all design parameters, across all difficulties, as well as all user settings.
\subsection{Fields}
The file contains a single JSON object with the fields \verb|users| and \verb|designParameters|. Users is a JSON object with a field for each user ID. Each field contains a user object with the fields and domains described in \ref{tab:settings_users}. The furthest level field is described in \ref{tab:per_difficulty_store}. Design parameters is a JSON object with a field for each design parameter, storing its value for each difficulty (described in \ref{tab:per_difficulty_store}). Its fields are described in \ref{tab:settings_design_parameters}. 
\begin{table}[H]
  \begin{center}
    \begin{tabularx}{\textwidth}{
        | >{\centering\arraybackslash\hsize=0.4\hsize}X
      | >{\centering\arraybackslash\hsize=0.6\hsize}X |}
      \hline
      \textbf{Field} & \textbf{Domain} \\
      \hline
      telemetryEnabled & Boolean \\
      \hline
      role & String (One of: PLAYER, DESIGNER, DEVELOPER) Note: field is unused. \\
      \hline
      furthestLevel & JSON object \\
      \hline
    \end{tabularx}
    \caption{User settings fields}
    \label{tab:settings_users}
  \end{center}
\end{table}
\begin{table}[H]
  \begin{center}
    \begin{tabularx}{\textwidth}{
        | >{\centering\arraybackslash\hsize=0.4\hsize}X
      | >{\centering\arraybackslash\hsize=0.6\hsize}X |}
      \hline
      \textbf{Field} & \textbf{Domain} \\
      \hline
      playerMaxHealth & JSON object(Per difficulty integer store)\\
      \hline
      shopItemCount & JSON object(Per difficulty integer store)\\
      \hline
      enemyDamageMultiplier & JSON object(Per difficulty real store)\\
      \hline
      enemyHealthMultiplier & JSON object(Per difficulty real store) \\
      \hline
      startingLives & JSON object(Per difficulty integer store)\\
      \hline
      maxMagic & JSON object(Per difficulty integer store)\\
      \hline
      magicGenerationRate & JSON object(Per difficulty integer store) \\
      \hline
    \end{tabularx}
    \caption{Design parameter fields}
    \label{tab:settings_design_parameters}
  \end{center}
\end{table}
\begin{table}[H]
  \begin{center}
    \begin{tabularx}{\textwidth}{
        | >{\centering\arraybackslash\hsize=0.4\hsize}X
      | >{\centering\arraybackslash\hsize=0.6\hsize}X |}
      \hline
      \textbf{Field} & \textbf{Domain} \\
      \hline
      EASY & D \\
      \hline
      MEDIUM & D\\
      \hline
      HARD & D \\
      \hline
    \end{tabularx}
    \caption{Per Difficulty Store (Of domain D)}
    \label{tab:per_difficulty_store}
  \end{center}
\end{table}
\subsection{Integrations}
\subsubsection{Java application}
The file is read once when a user is authenticated, capturing the user settings and design parameters at that time. The file is written to when the user toggles telemetry, changes a design parameter and saves this change. 
%TODO may add max level reached

\section{Logins File}

\subsection{Overview}
The logins file stores a JSON object that holds each user's role. It is used by the Python application to obtain the authenticated user's role. 
\subsection{Fields}
Each user ID is a field. All fields have the domain of String(One of: player, designer, developer).

\subsection{Integrations}

\subsubsection{Java application}
When authenticating a user the Java application makes a call to the python application, which then interacts with the file, as if it were authenticating a user. If a user is assigned a role by a developer, the Java application reads to file to find the user's ID, and if valid writes their new role. 

\subsubsection{Python Application}
When authenticating a user the Python application reads the file to find the given user ID, and on success reads their role. On failure, the Python application creates a new user with the ID provided by Google OAuth, who has the player role. 

\end{document}
