\subsection{Project Backlog}

\subsubsection{Sprint 1}

The project was split into three main sections representing the three main areas of work: the documentation, the Java application, and the Python application. Each of those areas is then further divided into epics and user stories. The epics and stories in this section include both those relevant to Sprint 1 and what is planned for Sprint 2. Due to the nature of Scrum, the epics for Sprint 2 may have adapted by the end of that sprint, and so may differ from the epics and stories in this prototype report.

\paragraph{Documentation}

\subparagraph{Report}

\paragraph{Stakeholders Can View Executive Summary}
As a stakeholder I need an executive summary to give me an insight into what is to come in the report and provide the most important details to me.

\paragraph{Stakeholders Can View Problem Framing}
As a stakeholder I need an in depth exploration of the problem so that I am informed of what problem the system should solve and ensure the development team fully understand the problem.

\paragraph{Stakeholders Can View Definition of Done}
As a stakeholder I need a definition of done so that it is clear to both the development team and I when work is done.

\paragraph{Stakeholders Can View Project Backlog}
As a stakeholder I need a project backlog so that I can determine what work is to be done in the project.

\paragraph{Stakeholders Can View Sprint One Prioritised Requirements}
As a stakeholder I need to know what requirements are being prioritised in Sprint One to know that they align with my priorities.

\paragraph{Stakeholders Can View Architecture Schema}
As a stakeholder I need to know the project schema so that I can understand how the application is structured and make informed decisions about future development.

\paragraph{Stakeholders Can View Data Flow Schema}
As a stakeholder I need to know the data flow schema so that I can understand how the data is structured and make informed decisions about future integration and use.

\paragraph{Stakeholders Can View Telemetry Schema}
As a stakeholder I need to know the telemetry schema so that I can understand how the telemetry is structured and make informed decisions about future integration and use.

\paragraph{Stakeholders Can View Game Design Documentation}
As a stakeholder I need to know the game design of the application so I can understand game mechanics and evaluate design decisions.

\paragraph{Stakeholders Can View Evaluation}
As a stakeholder I need to see a fair evaluation of the system so that I am made aware of its strengths and weaknesses.

\paragraph{Stakeholders Can View Sprint Two Prioritised Requirements}
As a stakeholder I need to see what requirements are being prioritised and planned for in Sprint Two so I can know they align with my priorities.

\paragraph{Stakeholders Can View Management}
As a stakeholder I need to see how the team has worked together and what roles each person took on during development so I can evaluate team performance.

\subparagraph{Process Information}

\paragraph{Stakeholders Can View Meeting Minutes}
As a stakeholder I need to be able to view who was at each weekly scrum meeting, what everyone did that scrum, what was discussed and what work is to be done so that I can remain up to date with project progress.

\paragraph{Stakeholder can view Risk Register}
As a stakeholder I need to be able to view a risk register of potential process risks so that I am aware of them and ensured they are being mitigated.

\subparagraph{Ethical and Legal Considerations}

\paragraph{Stakeholders Can View the Privacy and Data Protection Analysis}
As a stakeholder I need to be able to view how the system handles privacy and user data so that I can ensure it is in full legal compliance and minimises privacy risk.

\paragraph{Stakeholders Can View the Consent and Disclosure Analysis}
As a stakeholder I need the software to obtain user consent for the collection of data, and disclose to them what data is collected and why so that they can make informed decisions about their data.

\paragraph{Stakeholders Can View the Accessibility Analysis}
As a stakeholder I need to know in what ways accessibility has been considered and implemented within the software so that I can evaluate if it is sufficiently accessible.

\paragraph{Stakeholders Can View the Intellectual Property and Licensing Implications}
As a stakeholder I need to know what the licensing and intellectual property constraints of the software are so that I can use it in full legal compliance and honor the rights of the intellectual property owners.

\subparagraph{Project License}

\paragraph{Stakeholders Can View the Project License}
As a stakeholder I need to know what license the product falls under so that its usage complies with the license.

\subparagraph{Software and Data Inventory}

\paragraph{Maintainers Can View the Software Inventory}
As a maintainer I need to know what software is a direct dependency of the system as well as this software's license, provenance, cost model and the version in use, so that I can build, test, extend and maintain the system.

\paragraph{Maintainers Can View the Data Inventory}
As a maintainer I need to know what data the software directly depends on as well as this data's license, provenance, cost model and the version used, so I can build, test, extend and maintain the system.

\subparagraph{Deployment and Operations Guide}

\paragraph{Client can View the Java Application Deployment Instructions}
As a client I need instructions on how to deploy and operate the Java application so I can perform actions using it.

\paragraph{Client can View the Python Application Deployment Instructions}
As a client I need instructions on how to deploy and operate the Python application so I can perform actions using it.

\paragraph{Maintainer can View the Automated Test Running Instructions}
As a maintainer I need instructions on how to operate the automated test suite so that I can test any changes or extensions to the software to ensure their correctness.

\subparagraph{Test Evidence}

\paragraph{Stakeholder can View the Automated Test Evidence}
As a stakeholder I need evidence of the system passing automated tests so that I know the software runs correctly in the tested areas.

\paragraph{Stakeholder can View the End to End Test Evidence}
As a stakeholder I need evidence of the system passing end to end tests so that I know the software runs correctly in the tested areas.

\subparagraph{Presentation}

\paragraph{Stakeholder can View an Explanation of the Problem}
As a stakeholder I need to see that the group are aware of the problem the system will solve so that we both reach a point of understanding and agreement in relation to the problem.

\paragraph{Stakeholder can View the Design Approach}
As a stakeholder I need to see what approach the group took to solving the problem and how they designed their solution so that I can make an informed decision about its adoption, utility, and effectiveness.

\paragraph{Stakeholder can View Details of the Implementation}
As a stakeholder I need to see what path was taken to implement the product and how it was implemented so that I can understand the implementation and see why they made different decisions in relation to the implementation.

\paragraph{Stakeholder can View the Evaluation}
As a stakeholder I need to see an evaluation of the prototype so that I am informed of its advantages and limitations and thus can know its utility and where best to use it.

\paragraph{Stakeholder can View a Live Demonstration}
As a stakeholder I need to see a demonstration of the prototype so that I can see that it works, how to use it, and what it offers as well as to evidence what has been done in the project.

\paragraph{Stakeholder can View the Limitations and Next Steps}
As a stakeholder I need to see where the project is going to next so that I can see it will be improved in areas of limitation and that the group is on schedule to deliver the complete system.

\paragraph{Stakeholder can View the Ethics and Telemetry Disclosure}
As a stakeholder I need to see what the ethics of the system are, as well as its telemetry policy so that I can ensure the system complies with ethical and legal standards.

\paragraph{Stakeholders Can View Management Information}
As a stakeholder I need to know who took on which roles within the group so that I can evaluate how well each member fulfilled their role.

\paragraph{Stakeholders Can View a Brief of the Scrum Board}
As a stakeholder I need to be able to view a snapshot of the scrum board so that I can see it is being used to effectively manage the project.

\subparagraph{Maintenance and Troubleshooting Guide}

\paragraph{Maintainers Can View Maintenance Instructions}
As a maintainer I need clear maintenance instructions so I can ensure the game, settings, viewer and telemetry are functioning properly.

\paragraph{Users Can View Troubleshooting Instructions}
As a general user I need clear troubleshooting instructions based on clear and understandable error messages so that I can quickly troubleshoot errors and continue playing the game.

\paragraph{Maintainers Can View Extension Instructions}
As a maintainer I need to know what areas of the system should be the targets of extension and how to extend of the current system so that when the system needs extension those are done in the most appropriate way.

\subparagraph{Data Management Guide}

\paragraph{Stakeholders Can View What Data is Stored}
As a stakeholder I need to know what data is stored by the system so I can ensure this data is minimised and in full compliance with the law.

\paragraph{Maintainers Can View the Data Format}
As a maintainer I need to know what format the data is stored in so I can work with the stored data and extend what data is stored.

\subparagraph{Scrum Board}

\paragraph{Stakeholders Can View a Snapshot of the Scrum Board}
As a stakeholder I need to know what the completion status of each story is so that I can see they are being correctly managed and prioritised.

\paragraph{Stakeholders Can View a Snapshot of the Scrum Timeline}
As a stakeholder I need to know what the completion status of each epic is so that I can see they are being correctly managed and prioritised.

\paragraph{Python Application}

\subparagraph{Authentication and Access Control}

\paragraph{Users Can Log In}
As a general user I need to be able to log in with a username and password so that my account is securely authenticated and I am granted access to the application.

\paragraph{Users Can Reset their Login}
As a general user I need to be able to reset my login so that if I forget my login credentials I can recover my account by resetting them.

\paragraph{Users Can Perform Actions Permitted by Their Role}
As an authenticated user I need to perform only the actions permitted by my assigned role so that I cannot access functionality beyond my authority.

\paragraph{Users can view their Profile}
As an authenticated user I need to view my user information such as my username and role so that I am able to verify this information is correct and what I am expecting.

\subparagraph{Telemetry Views}

\paragraph{Designers Can View Funnel}
As a designer I need to be able to view a drop-off funnel showing completion rate for each stage based on simulated and user generated telemetry so that I can spot any stages with balancing issues.

\paragraph{Designers Can View Difficulty Spikes}
As a designer I need to be able to view which stages have disproportionately high failure rates and completion times from both simulated and user generated telemetry so that I can improve their balance.

\paragraph{Designers Can View Progress Curves}
As a designer I need to be able to view the time to complete and resource accumulation from both simulated and user generated telemetry events so that I can assess the balance of each stage.

\paragraph{Designers Can View Fairness Indicators}
As a designer I need to be able to compare key metrics from both user generated and simulated telemetry events across several different play styles so that I can assess if the game treats those play styles fairly.

\paragraph{Designers Can View Comparison Mode}
As a designer I need to be able to compare key metrics from both user generated and simulated telemetry events across all difficulties so that I can assess the balance of different difficulties.

\paragraph{Designers Can View Rule Based Design Suggestions}
As a designer I need the telemetry application to provide rule based design suggestions from both simulated and user generated telemetry so that it provides assistance in balancing the game.

\paragraph{Designers Can View Decision Log}
As a designer I need to be able to view a log of what design parameter changes have occurred along with an explanation as to why so that I can audit design decision.

\subparagraph{Telemetry Events}

\paragraph{Application Handles Start Session}
As a developer I need the application to validate and ingest start session events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Normal Encounter Fail}
As a developer I need the application to validate and ingest normal encounter fail events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Normal Encounter Complete}
As a developer I need the application to validate and ingest normal encounter complete events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Boss Encounter Start}
As a developer I need the application to validate and ingest boss encounter start events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Boss Encounter Fail}
As a developer I need the application to validate and ingest boss encounter fail events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Boss Encounter Complete}
As a developer I need the application to validate and ingest boss encounter complete events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Gain Coin}
As a developer I need the application to validate and ingest gain coin events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Buy Upgrade}
As a developer I need the application to validate and ingest buy upgrade events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles End Session}
As a developer I need the application to validate and ingest end session events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Settings Change}
As a developer I need the application to validate and ingest settings change events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\paragraph{Application Handles Kill Enemy}
As a developer I need the application to validate and ingest kill enemy events in real time, displaying clear errors when they are invalid, so the system can process them for analytics and exports.

\subparagraph{Seeded Dataset}

\paragraph{Developers Can Access a Telemetry Dataset}
As a developer I need a seeded dataset consisting of a large variety of telemetry events so that I can use it to test the telemetry application works.

\paragraph{Developers Can Access a Decision Dataset}
As a developer I need a set of sample balancing decisions within a sample decision log, that are a combination of good and bad decisions so that I can test the system is able to process the decision log.

\paragraph{Java Application}

\subparagraph{Authentication and Access Control}

\paragraph{Users Can Log In}
As a general user I need to be able to log in with a username and password so that my account is securely authenticated and I am granted access to the application.

\paragraph{Users Can Reset their Login}
As a general user I need to be able to reset my login so if I forget my login credentials I can recover my account by resetting them.

\paragraph{Users Can Perform Actions Permitted by Their Role}
As an authenticated user I want to perform only the actions permitted by my assigned role so that I cannot access functionality beyond my authority.

\subparagraph{Settings}

\paragraph{Users Can View the Telemetry Disclosure}
As a general user I need to be able to see what telemetry information is collected about me and it's purpose so that I am able to provide informed consent to the collection of my telemetry.

\paragraph{Users Can Toggle Telemetry}
As a general user I need a setting that allows me to enable and disable telemetry, that is enabled by default, so that I can withdraw my consent for the collection of telemetry events relating to my play.

\paragraph{Designers Can View and Change Starting Lives}
As a designer I need to be able to view and change the starting lives of the player for each difficulty so that I can balance the game.

\paragraph{Designers Can View and Change Enemy Health Multiplier}
As a designer I need to be able to view and change a multiplier for the amount of health enemies start each encounter with, for each difficulty so that I can balance the game.

\paragraph{Designers Can View and Change Player Maximum Health}
As a designer I need to be able to view and change the amount of health the player starts each encounter with, for each difficulty so that I can balance the game.

\paragraph{Designers Can View and Change Upgrade Price Multiplier}
As a designer I need to be able to view and change the multiplier applied to the cost of upgrades in the shop for each difficulty so that I can balance the game.

\paragraph{Designers Can View and Change Enemy Damage Multiplier}
As a designer I need to be able to view and change a multiplier for the amount of damage enemies deal each encounter, for each difficulty so that I can balance the game.

\paragraph{Designers Can View and Change Player Maximum Magic}
As a designer I need to be able to view and change the maximum amount of magic the player can have stored in an encounter, for each difficulty so that I can balance the game.

\paragraph{Designers Can View and Change Magic Regeneration Rate}
As a designer I need to be able to view and change the amount of magic the player regains at the start of each turn, for each difficulty so that I can balance the game.

\paragraph{Designers Can View and Change Number of Items in the Shop}
As a designer I need to be able to view and change the number of items available in the shop, for each difficulty so that I can balance the game.

\paragraph{Designers Can Execute a Simulated Run}
As a designer I need to be able to run a simulation of the game so that I can see what the effects of design decisions are on the game's balance.

\paragraph{Developers Can Assign Roles}
As a developer I need to be able assign roles to different users so that designers are given the designer role and developers are given the developer role, giving them the correct authorisation.

\subparagraph{Game Runs}

\paragraph{User can Chose Difficulty}
As a general user I need to be able to chose the difficulty of my run so that it is well balanced for my skill level.

\paragraph{Player can Use Mundane Attack Abilities}
As a player I need to be able to use any mundane attack abilities my character has (both purchased and default) to deal damage of a specific type to enemies so that I can defeat them.

\paragraph{Player can Chose Which Abilities to Purchase}
As a player I need to see a variety of abilities which I can purchase for my character with coins in between encounters so that I a can make meaningful decisions about what abilities to get.

\paragraph{Player Can Use Purchased Magic Attack Abilities}
As a player I need to be able to use any magic attack abilities my character has purchased from the shop, provided they have enough magic to use them, to deal damage of a specific type to enemies so that I can defeat them.

\paragraph{Enemies Can Use Attack Abilities}
As a player I need enemies to be able to use any attack abilities they have to deal damage of a specific type to my character, so that my character can die.

\paragraph{Player Benefits from Purchased Damage Reistance Passive Abilities}
As a player I need my character to take reduced damage of a specific type when they have purchased a passive ability from the shop that grants this, so that my character's durability is improved.

\paragraph{Player Benefits from Purchased Damage Boost Passive Abilities}
As a player I need my character to deal increased damage of a specific type when they have purchased a passive ability from the shop that grants this, so that my character's damage output is improved.

\paragraph{Enemies Have Damage Resistances and Vulnerabilities}
As a player I need some enemies to be resistant or vulnerable to damage of a specific type so that I am encouraged to think about which ability I use against them.

\paragraph{Players can Encounter Multiple Enemies in Combat}
As a player I need to encounter multiple enemies within a combat encounter so that I can chose which enemy to target strategically.

\paragraph{Players can Complete a Combat Round}
As a player I need to be able to complete a combat round after all enemies and my character have taken their turns, with my character regaining magic at the start of each round, so that I can fight enemies over multiple rounds and continue using magic abilities.

\paragraph{Players can Complete an Encounter}
As a player I need to be able to complete an encounter by killing all the enemies, gaining coins upon completion, so that I can progress to the shop.

\paragraph{Players can Retry an Encounter}
As a player I need to be able to retry an encounter if my character dies while having lives so that I can improve and potentially complete the encounter.

\paragraph{Players can Progress Through Stages}
As a player I need to be able to progress though the stages of the game, completing a stage after leaving the shop so that I can track my progression through the game and my character and enemies can gain power.

\paragraph{Players can Fail Runs}
As a player I need to be able to fail runs when my character dies without any lives, being sent back to stage one with no purchased abilities, so that there is consequence to my character dying.

\paragraph{Players can Complete Runs}
As a player I need to be able to complete a run by reaching the last stage and be shown a summary of my run once it's complete so that I can use this information to evaluate my performance in the run.

\subparagraph{Telemetry Events}

\paragraph{Application Handles Start Session}
As a developer I need the application to validate and write start session events to the event store so that I can view them externally.

\paragraph{Application Handles Normal Encounter Fail}
As a developer I need the application to validate and write normal encounter fail events to the event store so that I can view them externally.

\paragraph{Application Handles Normal Encounter Complete}
As a developer I need the application to validate and write normal encounter complete events to the event store so that I can view them externally.

\paragraph{Application Handles Boss Encounter Start}
As a developer I need the application to validate and write boss encounter start events to the event store so that I can view them externally.

\paragraph{Application Handles Boss Encounter Fail}
As a developer I need the application to validate and write boss encounter fail events to the event store so that I can view them externally.

\paragraph{Application Handles Boss Encounter Complete}
As a developer I need the application to validate and write boss encounter complete events to the event store so that I can view them externally.

\paragraph{Application Handles Gain Coin}
As a developer I need the application to validate and write gain coin events to the event store so that I can view them externally.

\paragraph{Application Handles Buy Upgrade}
As a developer I need the application to validate and write buy upgrade events to the event store so that I can view them externally.

\paragraph{Application Handles End Session}
As a developer I need the application to validate and write end session events to the event store so that I can view them externally.

\paragraph{Application Handles Settings Change}
As a developer I need the application to validate and write settings change events to the event store so that I can view them externally.

\paragraph{Application Handles Kill Enemy}
As a developer I need the application to validate and write kill enemy events to the event store so that I can view them externally.

\subsubsection{Sprint 2}

The project was split into three main sections representing the three main areas of work: the documentation, the Java application, and the Python application. Each of these areas is further divided into epics and user stories. The epics and stories in this section include both those relevant to Sprint 1 and Sprint 2. Due to the nature of Scrum, the epics for Sprint 2 may have adapted by the end of that sprint and may therefore differ from the epics and stories in this prototype report.

\subsection{Documentation}

\subsubsection{Report}

\paragraph{Stakeholders Can View Executive Summary}
As a stakeholder, I need an executive summary so that it gives me an insight into what is to come in the report and provides the most important details to me.

\paragraph{Stakeholders Can View Problem Framing}
As a stakeholder, I need an in-depth exploration of the problem so that I am informed of what problem the system should solve and can ensure the development team fully understands the problem.

\paragraph{Stakeholders Can View Definition of Done}
As a stakeholder, I need a definition of done so that it is clear to both the development team and me when work is done.

\paragraph{Stakeholders Can View Project Backlog}
As a stakeholder, I need a project backlog so that I can determine what work is to be done in the project.

\paragraph{Stakeholders Can View Sprint One Prioritised Requirements}
As a stakeholder, I need to know what requirements are being prioritised in Sprint One so that I know they align with my priorities.

\paragraph{Stakeholders Can View Architecture Schema}
As a stakeholder, I need to know the project schema so that I can understand how the application is structured and make informed decisions about future development.

\paragraph{Stakeholders Can View Data Flow Schema}
As a stakeholder, I need to know the data flow schema so that I can understand how the data is structured and make informed decisions about future integration and use.

\paragraph{Stakeholders Can View Telemetry Schema}
As a stakeholder, I need to know the telemetry schema so that I can understand how the telemetry is structured and make informed decisions about future integration and use.

\paragraph{Stakeholders Can View Game Design Documentation}
As a stakeholder, I need to know the game design of the application so that I can understand the game mechanics and evaluate design decisions.

\paragraph{Stakeholders Can View Evaluation}
As a stakeholder, I need to see a fair evaluation of the system so that I am made aware of its strengths and weaknesses.

\paragraph{Stakeholders Can View Sprint Two Prioritised Requirements}
As a stakeholder, I need to see what requirements are being prioritised and planned for in Sprint Two so that I know they align with my priorities.

\paragraph{Stakeholders Can View Management}
As a stakeholder, I need to see how the team has worked together and what roles each person took on during development so that I can evaluate team performance.

\subsubsection{Handover Pack}

\paragraph{Client Can View Application Deployment and Operation Instructions}
As a client, I need instructions on how to deploy and operate both applications so that I can perform actions using them.

\paragraph{Maintainer Can View Automated Test Running Instructions}
As a maintainer, I need instructions on how to operate the automated test suite so that I can test any changes or extensions to the software to ensure their correctness.

\paragraph{Maintainers Can View Maintenance Instructions}
As a maintainer, I need clear maintenance instructions so that I can ensure the game, settings, viewer, and telemetry are functioning properly.

\paragraph{Users Can View Troubleshooting Instructions}
As a general user, I need clear troubleshooting instructions based on understandable error messages so that I can quickly troubleshoot errors and continue playing the game.

\paragraph{Maintainers Can View Extension Instructions}
As a maintainer, I need to know what areas of the system should be the targets of extension and how to extend the current system so that, when the system needs extension, it is done in the most appropriate way.

\paragraph{Maintainers Can View Data Management Instructions}
As a maintainer, I need to see what data is collected and how it is managed so that I can use and integrate with it.

\subsubsection{Process Information}

\paragraph{Stakeholders Can View Meeting Minutes}
As a stakeholder, I need to be able to view who was at each weekly Scrum meeting, what everyone did that sprint, what was discussed, and what work is to be done so that I can remain up to date with project progress.

\paragraph{Stakeholder Can View Risk Register}
As a stakeholder, I need to be able to view a risk register of potential process risks so that I am aware of them and can ensure they are being mitigated.

\paragraph{Stakeholder Can View Scrum Board}
As a stakeholder, I need to be able to view the Scrum board so that I can see project progress and priorities, and ensure they meet expectations.

\subsubsection{Ethics and Licensing}

\paragraph{Stakeholders Can View the Privacy and Data Protection Analysis}
As a stakeholder, I need to be able to view how the system handles privacy and user data so that I can ensure it is in full legal compliance and minimises privacy risk.

\paragraph{Stakeholders Can View the Consent and Disclosure Analysis}
As a stakeholder, I need to see how the software handles consent and disclosure so that I know it is done in a legal and ethical manner.

\paragraph{Stakeholders Can View the Accessibility Analysis}
As a stakeholder, I need to know in what ways accessibility has been considered and implemented within the software so that I can evaluate whether it is sufficiently accessible.

\paragraph{Stakeholders Can View the Intellectual Property and Licensing Implications}
As a stakeholder, I need to know what the licensing and intellectual property constraints of the software are so that I can use it in full legal compliance and honour the rights of the intellectual property owners.

\paragraph{Stakeholders Can View the Project Licence}
As a stakeholder, I need to know what licence the product falls under so that its usage complies with that licence.

\paragraph{Maintainers Can View the Software and Data Inventory}
As a maintainer, I need to know what software is a direct dependency of the system, as well as each dependency's licence, provenance, cost model, and version in use, so that I can build, test, extend, and maintain the system.

\subsubsection{Technical Information}

\paragraph{Stakeholders Can View the Automated Test Evidence}
As a stakeholder, I need evidence of the system passing automated tests so that I know the software runs correctly in the tested areas.

\paragraph{Stakeholders Can View the End-to-End Test Evidence}
As a stakeholder, I need evidence of the system passing end-to-end tests so that I know the software runs correctly in the tested areas.

\paragraph{Stakeholders Can View Security Checklist}
TODO

\subsubsection{Presentation}

\paragraph{Stakeholder Can View an Explanation of the Problem}
As a stakeholder, I need to see that the group is aware of the problem the system will solve so that we can reach a point of understanding and agreement about the problem.

\paragraph{Stakeholder Can View the Design Approach}
As a stakeholder, I need to see what approach the group took to solving the problem and how they designed their solution so that I can make an informed decision about its adoption, utility, and effectiveness.

\paragraph{Stakeholder Can View Details of the Implementation}
As a stakeholder, I need to see what path was taken to implement the product and how it was implemented so that I can understand the implementation and see why different decisions were made.

\paragraph{Stakeholder Can View the Evaluation}
As a stakeholder, I need to see an evaluation of the prototype so that I am informed of its advantages and limitations and can know its utility and where it is best used.

\paragraph{Stakeholder Can View a Live Demonstration}
As a stakeholder, I need to see a demonstration of the prototype so that I can see that it works, how to use it, and what it offers, as well as to evidence the work done in the project.

\paragraph{Stakeholder Can View the Limitations and Next Steps}
As a stakeholder, I need to see where the project is going next so that I can see it will be improved in areas of limitation and that the group is on schedule to deliver the complete system.

\paragraph{Stakeholder Can View the Ethics and Telemetry Disclosure}
As a stakeholder, I need to see what the ethics of the system are as well as its telemetry policy so that I can ensure the system complies with ethical and legal standards.

\paragraph{Stakeholders Can View Management Information}
As a stakeholder, I need to know who took on which roles within the group so that I can evaluate how well each member fulfilled their role.

\paragraph{Stakeholders Can View a Brief of the Scrum Board}
As a stakeholder, I need to be able to view a snapshot of the Scrum board so that I can see it is being used to effectively manage the project.

\subsection{Python Application}

\subsubsection{Authentication and Access Control}

\paragraph{Users Can Log In}
As a general user, I need to be able to log in with a username and password so that my account is securely authenticated and I am granted access to the application.

\paragraph{Users Can Reset Their Login}
As a general user, I need to be able to reset my login so that if I forget my login credentials, I can recover my account.

\paragraph{Users Can Perform Actions Permitted by Their Role}
As an authenticated user, I need to perform only the actions permitted by my assigned role so that I cannot access functionality beyond my authority.

\paragraph{Users Can View Their Profile}
As an authenticated user, I need to view my user information, such as my username and role, so that I can verify it is correct and what I expect.

\subsubsection{Telemetry Views}

\paragraph{Designers Can View Funnel}
As a designer, I need to be able to view a drop-off funnel showing completion rates for each stage based on simulated and user-generated telemetry so that I can identify stages with balancing issues.

\paragraph{Designers Can View Difficulty Spikes}
As a designer, I need to be able to view which stages have disproportionately high failure rates and completion times from both simulated and user-generated telemetry so that I can improve their balance.

\paragraph{Designers Can View Progress Curves}
As a designer, I need to be able to view resource accumulation from both simulated and user-generated telemetry events, and time-to-complete for user-generated telemetry, so that I can assess the balance of each stage.

\paragraph{Designers Can View Fairness Indicators}
As a designer, I need to be able to compare key metrics from both simulated and user-generated telemetry across several different play styles so that I can assess whether the game treats those play styles fairly.

\paragraph{Designers Can View Comparison Mode}
As a designer, I need to be able to compare key metrics from both simulated and user-generated telemetry across all difficulties so that I can assess the balance between difficulties.

\paragraph{Designers Can View Rule-Based Design Suggestions}
As a designer, I need the telemetry application to provide rule-based design suggestions from both simulated and user-generated telemetry so that it assists in balancing the game.

\paragraph{Designers Can View Decision Log}
As a designer, I need to be able to view a log of what design parameter changes have occurred along with explanations of why they occurred so that I can audit design decisions.

\subsubsection{Telemetry Events}

\paragraph{Application Handles Start Session}
As a developer, I need the application to validate and ingest start session events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Normal Encounter Fail}
As a developer, I need the application to validate and ingest normal encounter fail events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Normal Encounter Complete}
As a developer, I need the application to validate and ingest normal encounter complete events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Boss Encounter Start}
As a developer, I need the application to validate and ingest boss encounter start events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Boss Encounter Fail}
As a developer, I need the application to validate and ingest boss encounter fail events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Boss Encounter Complete}
As a developer, I need the application to validate and ingest boss encounter complete events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Gain Coin}
As a developer, I need the application to validate and ingest gain coin events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Buy Upgrade}
As a developer, I need the application to validate and ingest buy upgrade events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles End Session}
As a developer, I need the application to validate and ingest end session events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Settings Change}
As a developer, I need the application to validate and ingest settings change events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\paragraph{Application Handles Kill Enemy}
As a developer, I need the application to validate and ingest kill enemy events in real time, displaying clear errors when they are invalid so that the system can process them for analytics and exports.

\subsubsection{Seeded Dataset}

\paragraph{Developers Can Access a Telemetry Dataset}
As a developer, I need a seeded dataset consisting of a variety of telemetry events so that I can test that the telemetry application works.

\paragraph{Developers Can Access a Decision Dataset}
As a developer, I need a set of sample balancing decisions within a sample decision log, containing a combination of good and bad decisions, so that I can test that the system can process the decision log.

\subsection{Java Application}

\subsubsection{Authentication and Access Control}

\paragraph{Users Can Log In}
As a general user, I need to be able to log in with a username and password so that my account is securely authenticated and I am granted access to the application.

\paragraph{Users Can Reset Their Login}
As a general user, I need to be able to reset my login so that if I forget my login credentials, I can recover my account by resetting them.

\paragraph{Users Can Perform Actions Permitted by Their Role}
As an authenticated user, I want to perform only the actions permitted by my assigned role so that I cannot access functionality beyond my authority.

\subsubsection{Settings}

\paragraph{Users Can View the Telemetry Disclosure}
As a general user, I need to be able to see what telemetry information is collected about me and its purpose so that I can provide informed consent to the collection of my telemetry.

\paragraph{Users Can Toggle Telemetry}
As a general user, I need a setting that allows me to enable and disable telemetry, enabled by default, so that I can withdraw my consent for the collection of telemetry events relating to my play.

\paragraph{Designers Can View and Change Starting Lives}
As a designer, I need to be able to view and change the starting lives of the player for each difficulty so that I can balance the game.

\paragraph{Designers Can View and Change Enemy Health Multiplier}
As a designer, I need to be able to view and change the multiplier for the amount of health enemies start each encounter with, for each difficulty, so that I can balance the game.

\paragraph{Designers Can View and Change Player Maximum Health}
As a designer, I need to be able to view and change the amount of health the player starts each encounter with, for each difficulty, so that I can balance the game.

\paragraph{Designers Can View and Change Encounter Payout}
As a designer, I need to be able to view and change the amount of coins gained when completing an encounter, for each difficulty, so that I can balance the game.

\paragraph{Designers Can View and Change Enemy Damage Multiplier}
As a designer, I need to be able to view and change the multiplier for the amount of damage enemies deal each encounter, for each difficulty, so that I can balance the game.

\paragraph{Designers Can View and Change Player Maximum Magic}
As a designer, I need to be able to view and change the maximum amount of magic the player can have stored in an encounter, for each difficulty, so that I can balance the game.

\paragraph{Designers Can View and Change Magic Regeneration Rate}
As a designer, I need to be able to view and change the amount of magic the player regains at the start of each turn, for each difficulty, so that I can balance the game.

\paragraph{Designers Can View and Change Number of Items in the Shop}
As a designer, I need to be able to view and change the number of items available in the shop, for each difficulty, so that I can balance the game.

\paragraph{Designers Can Execute a Simulated Run}
As a designer, I need to be able to run a simulation of the game so that I can see what the effects of design decisions are on the game's balance.

\paragraph{Developers Can Assign Roles}
As a developer, I need to be able to assign roles to different users so that designers are given the designer role and developers are given the developer role, giving them the correct authorisation.

\subsubsection{Game Runs}

\paragraph{User Can Choose Difficulty}
As a general user, I need to be able to choose the difficulty of my run so that it is well balanced for my skill level.

\paragraph{Player Can Use Mundane Attack Abilities}
As a player, I need to be able to use any mundane attack abilities my character has (both purchased and default) to deal damage of a specific type to enemies so that I can defeat them.

\paragraph{Player Can Choose Which Abilities to Purchase}
As a player, I need to see a variety of abilities that I can purchase for my character with coins between encounters so that I can make meaningful decisions about what abilities to get.

\paragraph{Player Can Use Purchased Magic Attack Abilities}
As a player, I need to be able to use any magic attack abilities my character has purchased from the shop, provided they have enough magic, to deal damage of a specific type to enemies so that I can defeat them.

\paragraph{Enemies Can Use Attack Abilities}
As a player, I need enemies to be able to use any attack abilities they have to deal damage of a specific type to my character so that my character can die.

\paragraph{Player Benefits From Purchased Damage Resistance Passive Abilities}
As a player, I need my character to take reduced damage of a specific type when they have purchased a passive ability from the shop that grants this so that my character's durability is improved.

\paragraph{Player Benefits From Purchased Damage Boost Passive Abilities}
As a player, I need my character to deal increased damage of a specific type when they have purchased a passive ability from the shop that grants this so that my character's damage output is improved.

\paragraph{Enemies Have Damage Resistances and Vulnerabilities}
As a player, I need some enemies to be resistant or vulnerable to damage of a specific type so that I am encouraged to think about which ability I use against them.

\paragraph{Players Can Encounter Multiple Enemies in Combat}
As a player, I need to encounter multiple enemies within a combat encounter so that I can choose which enemy to target strategically.

\paragraph{Players Can Complete a Combat Round}
As a player, I need to be able to complete a combat round after all enemies and my character have taken their turns, with my character regaining magic at the start of each round, so that I can fight enemies over multiple rounds and continue using magic abilities.

\paragraph{Players Can Complete an Encounter}
As a player, I need to be able to complete an encounter by killing all the enemies and gaining coins upon completion so that I can progress to the shop.

\paragraph{Players Can Retry an Encounter}
As a player, I need to be able to retry an encounter if my character dies while having lives so that I can improve and potentially complete the encounter.

\paragraph{Players Can Progress Through Stages}
As a player, I need to be able to progress through the stages of the game, completing a stage after leaving the shop so that I can track my progression through the game and my character and enemies can gain power.

\paragraph{Players Can Fail Runs}
As a player, I need to be able to fail runs when my character dies without any lives, being sent back to stage one with no purchased abilities, so that there is a consequence to my character dying.

\paragraph{Players Can Complete Runs}
As a player, I need to be able to complete a run by reaching the last stage and be shown a summary of my run once it is complete so that I can use this information to evaluate my performance in the run.

\subsubsection{Telemetry Events}

\paragraph{Application Handles Start Session}
As a developer, I need the application to validate and write start session events to the event store so that I can view them externally.

\paragraph{Application Handles Normal Encounter Fail}
As a developer, I need the application to validate and write normal encounter fail events to the event store so that I can view them externally.

\paragraph{Application Handles Normal Encounter Complete}
As a developer, I need the application to validate and write normal encounter complete events to the event store so that I can view them externally.

\paragraph{Application Handles Boss Encounter Start}
As a developer, I need the application to validate and write boss encounter start events to the event store so that I can view them externally.

\paragraph{Application Handles Boss Encounter Fail}
As a developer, I need the application to validate and write boss encounter fail events to the event store so that I can view them externally.

\paragraph{Application Handles Boss Encounter Complete}
As a developer, I need the application to validate and write boss encounter complete events to the event store so that I can view them externally.

\paragraph{Application Handles Gain Coin}
As a developer, I need the application to validate and write gain coin events to the event store so that I can view them externally.

\paragraph{Application Handles Buy Upgrade}
As a developer, I need the application to validate and write buy upgrade events to the event store so that I can view them externally.

\paragraph{Application Handles End Session}
As a developer, I need the application to validate and write end session events to the event store so that I can view them externally.

\paragraph{Application Handles Settings Change}
As a developer, I need the application to validate and write settings change events to the event store so that I can view them externally.

\paragraph{Application Handles Kill Enemy}
As a developer, I need the application to validate and write kill enemy events to the event store so that I can view them externally.
