\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{blindtext}
\usepackage[a4paper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\setcounter{secnumdepth}{4}
\usepackage{titlesec}

\usepackage[skip=6pt]{parskip}

\usepackage[backend=biber, style=ieee, sorting=none]{biblatex}
\addbibresource{bibliography.bib}
\usepackage[shortlabels]{enumitem}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true, allcolors=blue}
\usepackage[nameinlink,noabbrev,capitalize]{cleveref}
\usepackage{colortbl}
\usepackage[section]{placeins}
\usepackage{subcaption}
\usepackage{longtable}
\usepackage{comment}
\usepackage{caption}
\captionsetup{font=footnotesize}
\setlength{\parindent}{0pt}
\usepackage{titlesec}
\titlespacing*{\section} {0pt}{3ex}{2ex}
\titlespacing*{\subsection} {0pt}{3ex}{2ex}
\titlespacing*{\subsubsection} {0pt}{3ex}{2ex}
\usepackage{pdfpages}
\setlist{nolistsep,leftmargin=*}

\usepackage{tocloft}
\setlength{\cftsecindent}{0pt}
\setlength{\cftsubsecindent}{1.2em}
\setlength{\cftsecnumwidth}{2.2em}
\setlength{\cftsubsecnumwidth}{3.0em}
\setcounter{tocdepth}{2}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}
{}
{0pt}
{}

\usepackage{booktabs}

\usepackage{float}
\usepackage{tabularx}
\usepackage{wrapfig}

\title{Deployment and Operations\\[0.3em]
\large COM2020 - Project 7}
\author{Emre Acarsoy, Luca Croci, Tom Croft, Will Finney, Kazybek Khairulla, Luca Pacitti, \\ Harry Taylor}
\date{\today}
\begin{document}
\maketitle
\tableofcontents
\newpage
\section{Overview}
In this document we will outline first how to deploy both applications, and the test suite. We will then provide detailed operation instructions for both applications.

\section{Deployment}
\subsection{prerequisites}
To be able to follow and complete deployment, as well as operate the applications, the following are required.
\begin{itemize}
  \item Internet access
  \item A web browser
\end{itemize}

Internat access is assumed, most supported operating systems contain a web browser, however if one is not installed, firefox can be installed by following the steps \href{https://www.firefox.com/en-US/download}{here}.

\subsection{From Executable}
%TODO once KK packaged the apps
\subsubsection{Python Application}
\subsubsection{Java Application}

\subsection{From Source}
\subsubsection{Common}
These steps are required for both applications.

\begin{enumerate}
  \item Install python 3.13 or later. Instructions can be found \href{https://wiki.python.org/moin/BeginnersGuide/Download}{here}.
    \item Install requests: \verb|pip install requests|
  \item Setup environment variables. First obtain them from the email that is sent to all clients, then follow the below steps:
    \begin{itemize}
      \item On Windows run:
        \begin{enumerate}
            \item \verb|$env:OIDC_ISSUER="<ENVIRONMENT VARIABLE VALUE>"|
            \item \verb|$env:OIDC_CLIENT_ID="<ENVIRONMENT VARIABLE VALUE>"|
            \item \verb|$env:OIDC_CLIENT_SECRET="<ENVIRONMENT VARIABLE VALUE>"|
        \end{enumerate}
      \item On macOS or Linux run:
        \begin{enumerate}
            \item \verb|export OIDC_ISSUER="<ENVIRONMENT VARIABLE VALUE>"|
            \item \verb|export OIDC_CLIENT_ID="<ENVIRONMENT VARIABLE VALUE>"|
            \item \verb|export OIDC_CLIENT_SECRET="<ENVIRONMENT VARIABLE VALUE>"|
        \end{enumerate}
    \end{itemize}
\end{enumerate}

\subsubsection{Python Application}
\label{sec:python_src_deployment}
\begin{enumerate}
    \item Enter the telemetry directory: \verb|cd telemetry|
    \item Create a virtual environment: \verb|python3 -m venv venv|
  \item Activate the virtual environment:
    \begin{itemize}
        \item On windows: \verb|./venv/Scripts/Activate|
        \item On macOS or Linux: \verb|source venv/bin/activate|
    \end{itemize}
    \item Install packages: \verb|pip install -r requirements.txt|
  \item Run the program:
    \begin{itemize}
        \item On windows: \verb|python telemetry_app.py|
        \item On macOS or Linux: \verb|python3 telemetry_app.py|
    \end{itemize}
    \item To exit the venv run: \verb|deactivate|
\end{enumerate}

\subsubsection{Java Application}
\label{sec:java_src_deployment}
\begin{enumerate}
  \item Install java 17+. Instructions can be found \href{https://www.java.com/en/download/manual.jsp}{here}
  \item Install maven. Instructions can be found \href{https://maven.apache.org/install.html}{here}
    \item Enter the game directory \verb|cd game|
    \item Run \verb|mvn clean compile exec:java "-Dexec.mainClass=wizardquest.ui.GameRunPage"|
\end{enumerate}

\subsection{Test Suite}

\subsubsection{Python Application}
\begin{enumerate}
  \item Complete the deployment steps for the Python application in \ref{sec:python_src_deployment}
  \item While inside the virtual environment run: \verb|pytest|
\end{enumerate}
\subsubsection{Java Application}
\begin{enumerate}
  \item Complete the deployment steps for the Java application in \ref{sec:java_src_deployment}
  \item Run \verb|mvn test|
\end{enumerate}

\section{Operations}

\subsection{Python Application}

This section describes how to operate the Python telemetry app.

\subsubsection{Logging In}

When opening the application, a browser window will open, prompting the user to sign-in with their google account information. Once the user signs in successfully, the window can be closed. If the user has the role of "Developer" or "Designer", they will be granted access by the application.

\subsubsection{Navigation}

The navigation bar contains eight options: "Home", "Funnel", "Difficulty Spike", "Health", "Coins", "Time", "Suggestions" and "Decision Log". Clicking on one of these will navigate to the corresponding page. By default, the home page will be open.

\subsubsection{Home}

From the home page, the user is greeted with a welcome message and three options.

The first option is a dropdown menu which allows users to pick from viewing the telemetry data gathered from players, or the data gathered from simulated game runs.

The second option is to export gathered data to a .csv file. Either the player telemetry or simulated telemetry can be exported, depending on the selection on the dropdown menu.

The final option is to reset the data. Pressing this will open a confirmation dialog, and if the user confirms, all data corresponding to the dropdown selection will be deleted from the database.

\subsubsection{Telemetry Views}

\paragraph{Funnel View}

\paragraph{Difficulty Spike View}

\paragraph{Health View}

\paragraph{Coins View}

\paragraph{Time View}

\subsubsection{Suggestions}

\end{document}
